Synthesis of Linear Functional Programs

### 2021-07-23 article/article.tex
break line in example
moved example

@@

To further showcase the expressiveness of our synthesizer, we present as
examples the input and output program for \emph{reverse}.
Note how we can guide the synthesis using the assertion mechanism to 
supply an example:
{\small
\begin{minted}{haskell}
synth reverse :: List a -o List a -o List a
  | assert (reverse (Cons (1, Cons (2, Nil))) Nil) == (Cons (2, Cons (1, Nil))); 
\end{minted}

>>>>

To showcase the expressiveness of our synthesizer, we present as
examples the input and output program for \emph{reverse}.
Note how we can guide the synthesis using the assertion mechanism to 
supply an example:

{\small
\begin{minted}{haskell}
synth reverse :: List a -o List a -o List a
  | assert (reverse (Cons (1, Cons (2, Nil))) Nil) == (Cons (2, Cons (1, Nil))); 
\end{minted}

@@
